

title: "Statebins Using Data Visualization Technique [2019]"

date: "12/12/2018"


##1.Rental vacancy rate state bin 

```{r message=FALSE}
library(mdsr)
library(tidyr)
library(tidyverse)
library(readr)
library(statebins)
setwd("data visualization   651/project")
Rental_Vacancy <- read_csv("GeoFRED_Rental_Vacancy_Rate_by_State_Percent.csv")
Rental_Vacancy%>%arrange(desc(percent))
```

```{r}
library(readr)
GeoFRED_Rental_Vacancy_Rate_by_State_Percent <- read_csv("GeoFRED_Rental_Vacancy_Rate_by_State_Percent.csv")
GeoFRED_Rental_Vacancy_Rate_by_State_Percent
```

```{r}
##look at the structure of the data
str(Rental_Vacancy)
```


#####From the rental vacancy rate state bin map ,darker-colored states have a higher rental vacancy rates and lighter-colored states have a lower rates. The states that are ND,WY,AL have the higher vacancy rate among all other states .Most of the low vacancy rates ,that we can see from below state bin map ,are located mostly in west coast and east cost areas . It might be because of some population and immigration ,more job oppurtunities,more high-tech companies are almost located in these area and this trend makes rental vacancy rate lower than other states .

```{r}
library(statebins)
statebins(state_data = Rental_Vacancy,          
          state_col = "state", value_col = "percent",
          text_color = "black", breaks = 4,
          labels = c("3-6", "6-9", "9-12", "12-15"),
          brewer_pal="Blues", font_size = 3, legend_title="2017 Rental Vacancy Rate by State",legend_position="bottom")
```
##2.Death rate state bin 

```{r message=FALSE}
library(readr)
library(statebins)
library(tidyr)
library(tidyverse)
setwd("~/Desktop/data visualization /project")
death <- read_csv("GeoFRED_deaths_Rate_by_State_Percent.csv")
death%>%arrange(death_rate)


```


#####From the death rate state bin map ,darker-colored states have a higher death rates and lighter-colored states have a lower rates. The WV state has the highest death rate among all other states and the states that have  higher death rates are  almost located in the middle states of the US. If we compare this trend to east and west coast areas , we can easily find out that the death rate are much lower than middle states except ME.


```{r}
library(statebins)
statebins_continuous(state_data = death,
                     state_col = "state",
                     text_color = "black", value_col = "death_rate",
                     brewer_pal="OrRd", font_size = 3,
                     legend_title="Mortality Rate (2010)",
                     legend_position="bottom"
                    )
```






